\chapter{Backlogs}\label{backlog}

\section{Product Backlog}\label{product_backlog}

\begin{longtable}{|c|p{8cm}|c|}
    \caption*{Product Backlog} \\
    \hline
    \textbf{ID} & \textbf{User Story} & \textbf{Priority} \\
    \hline
    \endfirsthead
    
    \multicolumn{3}{c}%
    {{\bfseries \tablename\ \thetable{} -- continued from previous page}} \\
    \hline
    \textbf{ID} & \textbf{User Story} & \textbf{Priority} \\
    \hline
    \endhead

    \hline \multicolumn{3}{|r|}{{Continued on next page}} \\ \hline
    \endfoot

    \hline \hline
    \endlastfoot

    1 & Efficient Assistance for Challenging Concepts: Users can post questions and receive timely responses, facilitating efficient learning support. & High \\
    \hline
    2 & Comprehensive Learning Resources: The platform provides accessible and personalized learning resources, catering to diverse learning styles. & High \\
    \hline
    3 & Collaborative Peer Support: A space for meaningful academic discussions and peer support, fostering a sense of community. & Medium \\
    \hline
    4 & Seamless Collaborative Learning: Users can effortlessly form study groups, participate in discussions, and collaborate on academic tasks. & Medium \\
    \hline
    5 & Effective Time Management: Integration of a dedicated time management tool with features like task tracking, study logs, and personalized study plans. & Low \\
    \hline
    6 & Sign-in Functionality: Users should be able to sign in to the platform securely. & High \\
    \hline
    7 & Account Creation Feature: A user-friendly process for creating new accounts. & Medium \\
    \hline
    8 & Password Reset Capability: Users should have the option to reset their passwords. & Low \\
    \hline
    9 & User Profile Management: Users can edit and manage their profiles, enhancing personalization. & Medium \\
    \hline
    10 & Notification System: Implement a notification system to alert users about responses, updates, and relevant information. & Medium \\
    \hline
    11 & Voting Mechanism: Introduce a sophisticated voting system for assessing and prioritizing responses. & High \\
    \hline
    12 & Tag Subscription (Following): Users can subscribe to specific tags for a personalized feed of questions. & Medium \\
    \hline
    13 & Explore Page: A curated page showcasing a collection of questions for users to explore. & Low \\
    \hline
    14 & Camera Functionality: Integration of video and picture capabilities for visual content sharing. & Medium \\
    \hline
    15 & OCR Integration: Implement Optical Character Recognition (OCR) for efficient conversion of printed or handwritten text into digital content. & Low \\
\end{longtable}


\section{Sprint Backlog}\label{sprint_backlog}

\begin{table}[h]
    \centering
    \caption*{Sprint Backlog - Sprint 1}
    \begin{tabular}{|c|p{5cm}|c|}
        \hline
        \textbf{ID} & \textbf{Task} & \textbf{Estimate (hours)} \\
        \hline
        1 & Implement sign-in functionality & 8 \\
        \hline
        2 & Design user registration form & 5 \\
        \hline
        3 & Set up password reset functionality & 3 \\
        \hline
        6 & Sign-in Functionality: Users should be able to sign in to the platform securely. & 8 \\
        \hline
        7 & Account Creation Feature: A user-friendly process for creating new accounts. & 6 \\
        \hline
    \end{tabular}
\end{table}

\begin{table}[h]
    \centering
    \caption*{Sprint Backlog - Sprint 2}
    \begin{tabular}{|c|p{5cm}|c|}
        \hline
        \textbf{ID} & \textbf{Task} & \textbf{Estimate (hours)} \\
        \hline
        4 & User Profile Management: Implement user profile editing and management features & 10 \\
        \hline
        5 & Notification System: Develop a system to alert users about responses and updates & 8 \\
        \hline
        11 & Voting Mechanism: Integrate a sophisticated voting system for assessing and prioritizing responses & 12 \\
        \hline
        12 & Tag Subscription (Following): Implement the feature allowing users to subscribe to specific tags & 9 \\
        \hline
    \end{tabular}
\end{table}

\begin{table}[h]
    \centering
    \caption*{Sprint Backlog - Sprint 3}
    \begin{tabular}{|c|p{5cm}|c|}
        \hline
        \textbf{ID} & \textbf{Task} & \textbf{Estimate (hours)} \\
        \hline
        8 & Explore Page: Develop a curated page showcasing a collection of questions for users to explore & 6 \\
        \hline
        9 & Camera Functionality: Integrate video and picture capabilities for visual content sharing & 8 \\
        \hline
        10 & OCR Integration: Implement Optical Character Recognition (OCR) for efficient text conversion & 10 \\
        \hline
        13 & Explore Page: A curated page showcasing a collection of questions for users to explore. & 6 \\
        \hline
        14 & Camera Functionality: Integration of video and picture capabilities for visual content sharing. & 8 \\
        \hline
        15 & OCR Integration: Implement Optical Character Recognition (OCR) for efficient conversion of printed or handwritten text into digital content. & 10 \\
        \hline
    \end{tabular}
\end{table}
