\chapter{Project Proposal}\label{project_proposal}

\section{Problem Statement}\label{problem_statement}
The challenge at hand involves new students at SIT facing a \textbf{significant academic leap} from their previous educational experiences. The transition to university life brings forth various obstacles, including \textit{adapting to a different teaching style} and \textit{managing a more demanding workload}. This situation is a common struggle among \textbf{freshmen}, impacting their overall learning experience. The goal is to understand and address these challenges effectively by designing supportive educational systems and strategies that aid students in \textit{navigating the complexities of university life}, fostering a \textit{smoother transition}, and enhancing their learning journey.

\section{Implications}\label{implications}
Without proactive measures to support students in their transition to university life, there is a risk of \textbf{increased academic stress}, \textit{reduced satisfaction with the learning experience}, and potentially \textit{higher dropout rates}. Recognizing and addressing these challenges is crucial for the overall success and well-being of students, emphasizing the need for institutions to invest in \textit{tailored support systems}, \textit{mentorship programs}, and \textit{teaching methodologies} that facilitate a more seamless adaptation to the demands of higher education.
 
\section{Persona}\label{persona}

\begin{center}
\begin{longtable}{|l|p{10cm}|}
\hline
\textbf{Name} & Alex \\
\hline
\textbf{Age} & 19 \\
\hline
\textbf{Gender} & Male \\
\hline
\textbf{Program} & Computing Science \\
\hline
\textbf{Location} & Singapore Institute of Technology (SIT), Singapore\\
\hline
\textbf{Background} & Alex is the first in his family to step into the realm of higher education. He is enthusiastic about the opportunities that university life offers but is equally apprehensive about the academic hurdles that may come his way. \\
\hline
\textbf{Goals} & Alex aspires to attain a quality education that opens doors to promising career prospects. Additionally, he seeks to establish new connections, make friends, and engage in extracurricular activities for a well-rounded university experience. \\
\hline
\textbf{Pain points} & Alex is concerned about the rigorous academic workload in college, unsure of how to strike a balance between studies and social life. The prospect of making friends and fitting into the university environment adds to his worries. \\
\hline
\textbf{Other important information} & A diligent worker, Alex is determined to succeed in his academic journey. While slightly reserved, he is keen on overcoming shyness to build meaningful connections with his peers. \\
\hline
\end{longtable}
\end{center}


\section{Proposed Solution}\label{proposed_solution}

To address the challenges outlined in the problem statement, we present a comprehensive solution that integrates diverse functionalities designed to elevate the overall university experience.

Our proposed application adopts a forum-like structure, drawing inspiration from platforms such as Reddit and Instagram. This platform empowers students like Alex to pose questions and seek answers from peers. A sophisticated voting system will be incorporated to assess and prioritize responses. The application will embrace an Instagram-style interface, presenting users with a curated list of questions. Additional features include a "following" function for subscribing to specific tags, an "explore" page showcasing a collection of questions, and a user profile for efficient user management.

The key features include:

\subsection{Networking}

By leveraging APIs from Firebase and Google AI, we aim to establish a robust networking system, promoting seamless communication and information exchange among students, enhancing collaboration and community building.

\subsection{Database Management}

Our solution incorporates both SQLite and Firebase databases, ensuring a secure and efficient storage and retrieval system for essential information.

\subsection{Camera Functionality}

Recognizing the value of visual content, our app integrates video and picture capabilities. This empowers students to capture and share significant moments, enriching the documentation of experiences and creating a more engaging learning environment.

\subsection{Optical Character Recognition (OCR)}

To aid in academic workload management, we propose integrating OCR technology. This feature efficiently converts printed or handwritten text into digital content, facilitating the organization and accessibility of study materials.

These proposed functions collectively form a comprehensive and technologically advanced solution, addressing identified challenges and enhancing the overall university journey for students like Alex.

\section{Motivation}

The driving force behind this project lies in our dedication to improving the academic transition for students entering higher education. Understanding the common challenges freshmen encounter when adapting to the demands of university life, our aim is to facilitate a smooth transition by creating a platform where students can learn from each other online. Through the development of this application, we strive to provide a space for introverted students to express their queries and enable a collaborative environment where students can support each other in this transitional phase.

